---
title: "Dataset Preparation"
author: "Ran K"
date: "7/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Installing Packages

library(tidyverse)
library(stringr)
library(rvest)
```

# DataMining

All data was taken from [EsportEarning.com](www.esportsearnings.com) <br>
**A note** as of 07/24, I have decided to spilt the information into two files - <br>
File 1 - GeneralData.csv - a file with monthly earnings for each game. <br>
File 2 - HistoricalData.csv - a file with a data which is not time related like genre, release date and such.

## Mining part 1 - GeneralData.csv

First ill do some preparation.

```{r GeneralData.csv_prep}
nap <- function(){
  print("Napping")
  Sys.sleep(runif(1,2,3))
}

webpg1 <- read_html("https://www.esportsearnings.com/games/browse-by-genre")

# Preparing list of links for each game
link_list <- paste0("https://www.esportsearnings.com",webpg1 %>% html_nodes(".games_main_game_title a") %>% html_attr("href"))

# Preparing an empty df to directly recieve the data that I will mine
GeneralData <- data.frame()

```

Then comes the text mining

``` {r GeneralData.csv_mining}

Genres <- webpg1 %>%
  html_nodes(".games_main_genre_header span") %>%
  html_text()
# The Genres variable will need some treatment before we add it to the database

Game_stats <- webpg1 %>% html_nodes(".games_main_game_stats") %>% html_text()
# Game_stats variable will need some treatment before we add to the database

# Looping through each game and mining more information
for (i in 382:length(link_list)) {
  game_pg <- read_html(link_list[i])
  print(paste0("Scraping game number ",i))
  nap()
  # Name of game
  GeneralData[i,"Game"] <- game_pg %>% 
    html_node(".info_box_title") %>% 
    html_text()
  
  # Release date
  GeneralData[i,"ReleaseDate"] <- game_pg %>% 
    html_node(".format_row:nth-child(1) .info_text_value") %>% 
    html_text()
  
  # Online earnings
   GeneralData[i,"OnlineEarnings"] <- game_pg %>% 
     html_node(".detail_list_summary_box .highlight:nth-child(2) .detail_list_prize:nth-child(2)") %>% 
     html_text()

  # I dont manage to mine the offline earning line properly, so I wont include in the file and compute it by myself
  
  # Honestly only one of those is necessary but ill use both to verify that the total amount of earnings is valid
   
}  

```


Here I will deal with the variable that needs extra attention before entering it into our dataframe


``` {r GeneralData.csv_cleaning}

############################
# Treating and adding the Genres variable
############################

# Creating a varibale which will will contain the list of genres
GameGenres <- as.character()
# Using a loop i will duplicate the string indicating the
# Genre based on the number of games in each category

for (i in seq(1,length(Genres),2)) {
  temp <- as.numeric(regmatches(Genres[i+1],regexpr("\\d*",Genres[i+1])))
  GameGenres <- append(GameGenres,rep(Genres[i],temp))
}

# Adding to database.
GeneralData["Genre"] <- GameGenres
GeneralData$Genre <- as.factor(GeneralData$Genre)

##############################
# Treating Game_stats variable
##############################

# As Game_stats  is actully a string containing 3 different variables, ill split it first then add to the database.
# Splitting into 3 variables

TotalEarnings <- regexpr("(?<=\\$)(.*?)\\.\\d{2}",Game_stats,perl = TRUE)
TotalEarnings <- regmatches(Game_stats,TotalEarnings)
TotalPlayers<- regexpr("(?<=\\d{2})\\d*(?= Pl)",Game_stats,perl = TRUE)
TotalPlayers <- regmatches(Game_stats,TotalPlayers)
TotalTournaments <- regexpr("(?<=ers|er)\\d*(?= T)",Game_stats,perl = TRUE)
TotalTournaments <- regmatches(Game_stats,TotalTournaments)

# Adding the variables into the database

GeneralData["TotalEarnings"] <- TotalEarnings
GeneralData["TotalPlayers"] <- TotalPlayers
GeneralData["TotalTournaments"] <- TotalTournaments

# Fixing a small typo in the release date
GeneralData[which(GeneralData$ReleaseDate==11),"ReleaseDate"] <- 2011

# Removing a duplicate line of the game Battalion 1944
GeneralData <- GeneralData[-which(GeneralData$Game== "Battalion 1944" & GeneralData$TotalTournaments == 0),]

############################
# Removing unwarted characters and doing some last manupulations
############################

GeneralData$OnlineEarnings <- as.numeric(gsub("[\\$,]","",GeneralData$OnlineEarnings))
GeneralData$TotalEarnings <- as.numeric(gsub("[\\$,]","",GeneralData$TotalEarnings))
GeneralData$TotalPlayers <- as.numeric(GeneralData$TotalPlayers)
GeneralData$TotalTournaments <- as.numeric(GeneralData$TotalTournaments)

#Reordering columns
col_order_General <- c("Game","ReleaseDate","Genre","TotalEarnings","OnlineEarnings","TotalPlayers","TotalTournaments")
GeneralData <- GeneralData[,col_order_General]

#Removing extra variables
rm(TotalEarnings,TotalPlayers,TotalTournaments)

```


```{r GeneralData.csv_saving}

write.csv(GeneralData,"GeneralEsportData.csv", row.names = FALSE)

```


## Mining Part 2 - Monthly historical information


```{r HistoricalData.csv_mining}
HistoricalData <- data.frame()
for (i in 1998:2020) {
  for (j in 1:12) {
  print(paste0("Mining historical data from ",j,"/",i))
  nap()
  webpg2 <- read_html(paste0("https://www.esportsearnings.com/history/",i,"-",j,"/games"))
  games <- webpg2 %>% html_nodes(".detail_list_player a") %>% html_text()
  
  prizepool <- webpg2 %>% html_nodes(".detail_list_player+ .detail_list_prize") %>% html_text()
  prizepool <- as.numeric(gsub("[\\$,]","",prizepool))
  
  players <- webpg2 %>% html_nodes(".detail_list_prize:nth-child(4)") %>% html_text()
  players <- as.numeric(gsub("\\D","",players))
  
  tournaments <- webpg2 %>% html_nodes(".detail_list_prize~ .detail_list_prize+ .detail_list_prize") %>% html_text()
  tournaments <- as.numeric(gsub("\\D","",tournaments))
  
  date <- paste0(j,"/",i)
  date <- rep(date, length(games))
  temp <- data.frame(Date = date, Earnings = prizepool, Players = players,
                        Tournaments = tournaments, Game = games)
  
  HistoricalData <- rbind(HistoricalData,temp)
  }
}
rm(temp) #removing temporary df
```


```{r HistoricalData.csv_cleaning}
# Reformatting dates
HistoricalData$Date <- paste0("01/",HistoricalData$Date)
HistoricalData$Date <- as.Date(HistoricalData$Date, format = "%d/%m/%Y")

#Reordering columns
col_order_Historical <- c("Date","Game","Earnings","Players","Tournaments")
HistoricalData <- HistoricalData[,col_order_Historical]

```


```{r HistoricalData.csv_saving}

write.csv(HistoricalData,"HistoricalEsportData.csv", row.names = FALSE)

```


All done












