---
title: "Dataset Preparation"
author: "Ran K"
date: "7/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Installing Packages

library(tidyverse)
library(stringr)
library(rvest)
```

# DataMining

All data was taken from [EsportEarning.com](www.esportsearnings.com)

## Mining part 1 - general information

First ill do some preparation.

```{r mining_part_1_prep}
webpg1 <- read_html("https://www.esportsearnings.com/games/browse-by-genre")

#Preparing list of links for each game
link_list <- paste0("https://www.esportsearnings.com",webpg1 %>% html_nodes(".games_main_game_title a") %>% html_attr("href"))

#Preparing an empty df to directly recieve the data that I will mine
temp_df1 <- data.frame()

```

Then comes the text mining

``` {r mining_part_1_mining}

genres <- webpg1 %>%
  html_nodes(".games_main_genre_header span") %>%
  html_text()
#The genres variable will need some treatment before we add it to the database

#Looping through each game and mining more information
for (i in 1:length(link_list)) {
  game_pg <- read_html(link_list[i])
  
  #Name of game
  temp_df1[i,"Name"] <- game_pg %>%
    html_node(".info_box_title") %>%
    html_text()
  
  #Release date
  temp_df1[i,"ReleaseDate"] <- game_pg %>%
    html_node(".format_row:nth-child(1) .info_text_value") %>%
    html_text()
  
  #Largest tournement prize pool (will be taken from the game webpage)
  temp_df1[i,"LargestPrizePool"] <- game_pg %>%
    html_node(".highlight:nth-child(2) .detail_list_tournament+ .detail_list_prize") %>%
    html_text()
  
}  

```

Here I will deal with the variable that needs extra attention before entering our dataframe

``` {r mining_part_1_cleaning}

############################
#Treating and adding the genre variable
############################

#Creating a varibale which will will contain the list of genres
gameGenres <- as.character()
#using a loop i will duplicate the string indicating the
# genre based on the number of games in each category

for (i in seq(1,length(genres),2)) {
  temp <- as.numeric(regmatches(genres[i+1],regexpr("\\d*",genres[i+1])))
  gameGenres <- append(gameGenres,rep(genres[i],temp))
}

# Adding to database.
temp_df1["genre"] <- gameGenres

```

## Mining Part 2 - Historical information

You can also embed plots, for example:

```{r mining_part_2}
temp_df2 <- data.frame()
for (i in 1998:2020) {
  
  
  webpg2 <- read_html(paste0("https://www.esportsearnings.com/history/",i,"/games"))
  games <- webpg2 %>% html_nodes(".detail_list_player a") %>% html_text()
  
  prizepool <- webpg2 %>% html_nodes(".detail_list_player+ .detail_list_prize") %>% html_text()
  prizepool <- as.numeric(gsub("[\\$,]","",prizepool))
  
  players <- webpg2 %>% html_nodes(".detail_list_prize:nth-child(4)") %>% html_text()
  players <- as.numeric(gsub("\\D","",players))
  
  tournaments <- webpg2 %>% html_nodes(".detail_list_prize~ .detail_list_prize+ .detail_list_prize") %>% html_text()
  tournaments <- as.numeric(gsub("\\D","",tournaments))
  
  year <- webpg2 %>% html_nodes("h1") %>% html_text()
  year <- gsub("\\D","",year)
  year <- rep(year, length(games))
  temp <- data.frame(Year = year, Earnings = prizepool, Players = players,
                        Tournaments = tournaments, Game = games)
  
  temp_df2 <- rbind(temp_df2,temp)
  
}
```

# Database Preparation

Here ill connenct the two temporary dataframe to form the final database.

```{r df_preparation}

df_final <- temp_df2

for (i in 1:nrow(df_final)) {
  df_final[i,"ReleaseDate"] <- 
    temp_df1[match(df_final[i,"Game"],temp_df1[,"Name"]),"ReleaseDate"]
  df_final[i,"Genre"] <- 
    temp_df1[match(df_final[i,"Game"],temp_df1[,"Name"]),"genre"]
}

#Fixing an error
df_final[which(df_final$ReleaseYear==11),"ReleaseDate"] <- 2011 #checked online

#Reordering columns
col_order <- c("Year","Game","ReleaseDate","Genre","Earnings","Players","Tournaments")
df_final <- df_final[,col_order]

df_final$Genre <- as.factor(df_final$Genre)
```

```{r save_to_csv}

write.csv(df_final,"EsportsEarnings_final.csv", row.names = FALSE)

```



All done












